### 2022-08-26 manuscript.Rmd
Proof-reading

  Number of words: 251 (abstract), 842 (introduction), 1,847 (discussion)

@@

Taken together, the present study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on our visual processing of this object.
The immediacy of this influence is remarkable in at least two different ways:
First, it does not require extensive training but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (≥ 400 ms), typically associated with semantic processing, but also at much earlier stages (≤ 200 ms), typically associated with visual perception itself.

>>>>

  Number of words: 212 (abstract), 849 (introduction), 1,856 (discussion)

@@

Taken together, the present study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on our visual processing of this object.
The immediacy of this influence is remarkable in at least two different ways:
First, it does not require extensive training but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at much earlier stages (< 200 ms), typically associated with visual perception itself.
